DATA 624 Homework 1

### 2020-02-05 DATA624/HW1.Rmd
More work on HW1

---
title: "DATA 624 Homework 1"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "hide"
---

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

---
title: "DATA 624 Homework 1"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
    toc_depth: 3
    code_folding: "show"
---

@@

**`gold` is an annual time series, `woolyrnq` is a quarterly time series and `gas` is a monthly time series**

@@

**One-family home sales in the US tend to be highest in March.  The ACF plot suggests that there is some annual cycle, but it is noisy.**

@@

**If I am a realtor I'm not going to be busy in the winter months.  Early spring (march through may) will be my busy time of the year.**

@@

**There appears to be a monthly pattern to the data.**

@@

**Accidental deaths in the US tends to be highest in July.**

@@

**There isn't much variation from Q2 through Q4.  The trend was genrally increasing until about the 1980's.**

@@

**Q1 is a slow quarter for Australian clay brick producers.  There has been quite a bit more irregularity since 1975.**

@@

**There appears to be a cycle in the data.  It looks like it's about a 10 to 11 year cycle.**

@@

**If the pattern holds 2020 should be a year with low sunspot area.**
